---
title: "AI-PS package notebook"
output: html_notebook
---
setting working directory
```{r}
knitr::opts_knit$set(root.dir = normalizePath("/Users/kanferg/Desktop/Gil_LabWork/Gil_packages/AIPS_Package/Example_images/sgPINKvsWT/"))
```


Parkin expressing cells treated with CCCP are loaded
```{r}
frame<-load_image(Image_File_name="Image_1.tif",path="/Users/kanferg/Desktop/Gil_LabWork/Gil_packages/AIPS_Package/Example_images/sgPINKvsWT/",minmax_nrom=TRUE)
```

The variable object is a list of two channel
Parkin-GFP in channel-1 and dapi staining for channel-2

```{r}
display(abind(frame$CH1*5,frame$CH2,along = 1),method = "raster")
```
```{r, figures-side, fig.show="hold", out.width="25%"}
#par(mar = c(4, 4, .1, .1))
plot(frame$CH1*5)
plot(frame$CH2)
```



First the nucleus will be segmented using the Nucleus_segmentation function. 

```{r}
nuc_mask<-Nucleus_segmentation(x=frame$CH2,intens=1,filter_size=10,offset=0.04,opensize=3,
                               rmObjects_small=30,Use_watershed=TRUE,distmap_value=2,rm_outliers=TRUE,Out_P=0.95,
                               Masks_display=TRUE)
seg_disp = paintObjects(nuc_mask$mask_nuc, toRGB(frame$CH2), opac=c(1, 1),col=c("red",NA),thick=TRUE,closed=TRUE)
plot(seg_disp)
```



Than the GFP-Parkin will be segmented using the nuc_mask as the seed. The function retrieved a list composed of roi pixel coordination of the center of ecth cell and a table and two maks one for the cytosle and the other for the nuclues.  

```{r}
GFP_mask<-Cytosol_segmentation(x=frame$CH1,y=nuc_mask$mask_nuc,intens=5,filter_size=10,offset=0.1,mat_size_smooth=19,opensize=7,rmObjects_large=30000,Use_watershed=TRUE)

seg<-paintObjects(GFP_mask$mask_cyto,paintObjects(GFP_mask$mask_nuc,toRGB(frame$CH1*5),opac=c(1,1),col=c("red",NA)),opac=c(1,1),col=c("green",NA),thick=TRUE,closed=TRUE)  
plot(seg)
```
SVM model is created by picking cells which lost Parkin mitochondrial recruitment. These cells are labeled Positive. The function returns a feture_table contains 20 detures extracted from the segmented cells. 

```{r}
Features_Table<-Feature_extract(x=frame$CH1,mask_cyto=GFP_mask$mask_cyto,label_class="Postive")
head(Features_Table$Ts.mix)
```
Picking phenotype exampled cells. The cells which Parkin mitochondrial translocation is abolished are labeled as postive cells for corresponding fetures marking. 

```{r}
Table_training<-Pick_cells(mask_nuc=GFP_mask$mask_nuc,x=frame$CH1,Ts.mix=Features_Table$Ts.mix,intens=5,parameters_nuc=GFP_mask$parameters_nuc,font_size=0.7,label_class="Postive",Masks_display=TRUE)
head(Table_training$Table_class_train)

```
```{r}
plot(Table_training$seg_class_sel)
```
The data created will be assigned in to SVM algorithm and the accuracy of linaer karnel versus non-liner karnel is compered. 
All the tables shoud be save to the Table-training repository 
```{r}
head(table)
```


First we mesure acurrrecy for Linear Kerenel
```{r}
acc<-Model_svm(Table_class_train=table,kernel_linear=TRUE,cost=10, degree = 45)
print(mean(acc))
```
non liner kernel 

```{r}
acc<-Model_svm(Table_class_train=table,kernel_linear=FALSE,cost=10, degree = 45)
print(mean(acc))
```

Thea a PCA analysis for selecting features 

```{r}
PCA_plot<-Fetures_PCA(Table_class_train=table,cartesian_lim_x=c(-15,10),cartesian_lim_y =c(-20,20),font_size=14)
PCA_plot
```

SVM model save and features selectopn acording to the PCA output

```{r}
model<-SVM_FeatureSel(Table_class_train=table,kernel_linear=FALSE,cost= 10, degree = 45)
print(mean(model$ACC))
```

For deploy svm model and creat a mask first Nucls and cytosole will be segmented and than the model will be deploy


##Deployment SVM 


```{r}
frame<-load_image(Image_File_name="Image_2.tif",path="/Users/kanferg/Desktop/Gil_LabWork/Gil_packages/AIPS_Package/Example_images/sgPINKvsWT/",minmax_nrom=TRUE)
nuc_mask<-Nucleus_segmentation(x=frame$CH2,intens=1,filter_size=10,offset=0.04,opensize=3,
                               rmObjects_small=30,Use_watershed=TRUE,distmap_value=2,rm_outliers=TRUE,Out_P=0.95,
                               Masks_display=TRUE)
GFP_mask<-Cytosol_segmentation(x=frame$CH1,y=nuc_mask$mask_nuc,intens=5,filter_size=10,offset=0.1,mat_size_smooth=19,opensize=7,rmObjects_large=30000,Use_watershed=TRUE)
seg<-paintObjects(GFP_mask$mask_cyto,paintObjects(GFP_mask$mask_nuc,toRGB(frame$CH1*5),opac=c(1,1),col=c("red",NA)),opac=c(1,1),col=c("green",NA),thick=TRUE,closed=TRUE)  
plot(seg)
Features_Table<-Feature_extract(x=frame$CH1,mask_cyto=GFP_mask$mask_cyto,label_class="Postive")
```

Now the model and the features selection will be used for the deploy and the genration of called cell mask

```{r}
Target_mask<-maskGen_deploySVM(x=GFP_mask$mask_cyto,y=GFP_mask$mask_nuc,model=model$model,Table_class_train=Features_Table$Ts.mix,label_class="Postive",erode_mask=T,opensize=9,Sel=TRUE,Selected_Features=model$Selected_Features,TH=0)
display(frame$CH1,"raster")
celltext<-text(x= data.frame(Target_mask$table)["m.cx"][,1], y= data.frame(Target_mask$table)["m.cy"][,1], labels=data.frame(Target_mask$decision_values)[,1], col="yellow", cex = 0.8)

```

The selected cells which will get photoactivated

```{r}
disp_call<-paintObjects(Target_mask$mask,toRGB(frame$CH1*2),opac=c(1,1),col=c("red",NA),thick=TRUE,closed=TRUE)  
plot(disp_call)
```




```{r}

```

